Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-09-05 Manuscript.Rmd

We performed a coordinate-based meta-analysis to limit the network search space to a set of overlapping and unique standard regions [@Glasser2016] across DMN and SV literatures. Using each literature's mean number of reports per area as the null probability, one-way chi-squared tests of proportions were used to identify regions that were significantly present in their respective literatures. The resulting lists were used to identify the set of overlapping brain areas. Unique areas were then determined by permuting the affiliation of each study (i.e. DMN or SV) to create a null distribution of chi-squared statistics, which as used to identify regions more often reported in either literature.

>>>>

We performed a coordinate-based meta-analysis to limit the network search space to a set of overlapping and unique standard regions [@Glasser2016] across DMN and SV literatures (see Methods). Using each literature's mean number of reports per area as the null probability (DMN = ; SV = ), one-way chi-squared tests of proportions were used to identify regions that were significantly present in their respective literatures. The resulting lists were used to identify the set of common brain areas. Unique areas were then determined by permuting the affiliation of each study (i.e. DMN or SV) to create a null distribution of chi-squared statistics, which as used to identify regions more often reported in either literature.
